\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-06 analysis/paper/paper.Rmd
working on table with taxon info

>>>>

```{r taxonTable, message = FALSE, echo = FALSE}
df <- data.frame(taxonCode = c("ABBA", "ABLAL", "ACRU, ACRUR", "ACSAS, ACSA3", 
                               "AMLA", "ARTR2", "BELE", "BENE4", "CACA18", "CAOV2",
                               "CATO6", "CELA", "CODR", "FRAM2", "FRPE"),
                 scientificName = c("*Abies balsamea*", "*Abies lasiocarpa*", "*Acer rubrum*",
                                    "*Acer saccharum*", "*Amelanchier laevis*", "*Artemisia tridentata*",
                                    "*Betula lenta*", "*Betula neoalaskana*", "*Carpinus caroliniana*",
                                    "*Carya ovata*", "*Carya tomentosa*", "*Celtis laevigata*", 
                                    "*Cornus drummondii*", "*Fraxinus americana*", "*Fraxinus pennsylvanica*"),
                 commonName = c("balsam fir", "subalpine fir", "red maple", "sugar maple",
                                "Allegheny serviceberry", "sagebrush", "sweet birch", "resin birch",
                                "American hornbeam", "shagbark hickory", "mockernut hickory",
                                "sugarberry", "roughleaf dogwood", "white ash", "green ash"),
                 count = c(47,117, 489, 79, 37, 494, 28, 35, 170, 46, 134, 179, 31, 20, 92))

knitr::kable(x = df, 
             # set column names
             col.names = c("Taxon code",
                           "Scientific name *(Genus species)*",
                           "Common name",
                           "Number of spectra"),
             # center align text in the columns
             align = c("l", "l", "l", "l"),
             format = "simple")
```
